### 2014-03-15 src/analysis.Rnw
Fix column names to use correct letters

<<xpercentunit>>=
#1
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xselround}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results.}
\label{tbl:xselceil}
\end{table*}

@@

<<count>>=
#2
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:lcountl}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\caption {The line count selection criteria results (within).}
\label{tbl:lcountw}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operators}
\label{tbl:operators}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}

>>>>

<<xpercentunit>>=
#1
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xselround}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results.}
\label{tbl:xselceil}
\end{table*}

@@

<<count>>=
#2
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:lcountl}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\caption {The line count selection criteria results (within).}
\label{tbl:lcountw}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {Operators}
\label{tbl:operators}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}

### 2014-03-15 src/paper.Rnw
Fix column names to use correct letters

sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

>>>>

sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', '$R^2$',      '$\\mu_{red}$',            '$\\sigma_{red}$',         'num',    '$\\beta_1$')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
